`gosset`: An R package for analysis and synthesis of ranking data in agricultural

### 2022-06-24 inst/paper/paper.Rmd
update manuscript

---
title: '`gosset`: An R package for analysis and synthesis of ranking data in agricultural experimentation'
abstract: null
output: 
   pdf_document:
     fig_caption: true
     number_sections: false
     keep_tex: false
latex_engine: pdflatex
#output:
# word_document: default
editor_options:
  markdown:
    wrap: 72
bibliography: paper.bib
csl: apa.csl
header-includes:
  - \usepackage{pdfpages}
  - \usepackage{caption}
  - \usepackage{xcolor}
  - \captionsetup[figure]{font=small}
  - \captionsetup[table]{font=small}
---

@@

To consider the effect of climate factors on variety performance, we used the climatic covariates to fit a 
Plackett-Luce tree. For brevity, we used the variables maximum nighttime temperature (maxNT) and  maximum daytime temperature, but more variables can be used in a Plackett-Luce tree. Temperature data were obtained from the NASA POWER dataset, using the R package *nasapower* [@nasapower]. The temperature data downloaded from NASA POWER were used for computing the climatic variables with the package *climatrends* [@climatrends]. In this case, we only use the rankings corresponding to the overall performance of varieties.

@@

pld <- cbind(R, temp)

pl <- pltree(R ~ maxNT + maxDT, 
             alpha = .05,
             data = pld)
```

The following is an example of the plot made with the function ``plot`` in the gosset package.
```{r , message=FALSE, eval=FALSE, echo=TRUE}

plot.pltree(pl)

>>>>

---
title: '`gosset`: An R package for analysis and synthesis of ranking data in agricultural
  experimentation'
abstract: null
output:
  word_document: default
  pdf_document:
    fig_caption: yes
    number_sections: no
    keep_tex: no
latex_engine: pdflatex
editor_options:
  markdown:
    wrap: 72
bibliography: paper.bib
csl: apa.csl
header-includes:
- \usepackage{pdfpages}
- \usepackage{caption}
- \usepackage{xcolor}
- \captionsetup[figure]{font=small}
- \captionsetup[table]{font=small}
---

@@

To consider the effect of climate factors on variety performance, we used climatic covariates to fit a 
Plackett-Luce tree. For brevity, we used the variables maximum nighttime temperature (maxNT) and  maximum daytime temperature, but more variables can be used in a Plackett-Luce tree. Temperature data were obtained from the NASA POWER dataset, using the R package *nasapower* [@nasapower]. The temperature data downloaded from NASA POWER were used for computing the climatic variables with the package *climatrends* [@climatrends]. In this case, we only use the rankings corresponding to the overall performance of varieties.

@@

pld <- cbind(R, nicabean_temp_ind)

pl <- pltree(R ~ ., 
             alpha = .9,
             data = pld)
```

The following is an example of the plot made with the function ``plot`` in the gosset package.
```{r , message=FALSE, eval=FALSE, echo=TRUE}
plot(pl)

```
!["Plackett-Luce tree plot with gosset function *plot*"](pltree_01.png)
